---
title: "Ch. 21 Iteration"
author: "Jerri Schorr"
date: 12-10-2019
output: github_document
---

##### **Chapter 21**

###### **21.1**

* 3 benefits

    + It’s easier to see the intent of your code, because your eyes are drawn to what’s different, not what stays the same.

    + It’s easier to respond to changes in requirements. As your needs change, you only need to make changes in one place, rather than remembering to change every place that you copied-and-pasted the code.

    + You’re likely to have fewer bugs because each line of code is used in more places.

```{r}
library(tidyverse)
```

###### **21.2**

```{r}
df <- tibble(
  a = rnorm(10),
  b = rnorm(10),
  c = rnorm(10),
  d = rnorm(10)
)

output <- vector("double", ncol(df))  # 1. output
for (i in seq_along(df)) {            # 2. sequence
  output[[i]] <- median(df[[i]])      # 3. body
}
output
```

* every loop has an output, body, and sequence

###### **21.3**

* There are four variations on the basic theme of the for loop:

    + Modifying an existing object, instead of creating a new object.

    + Looping over names or values, instead of indices.

    + Handling outputs of unknown length.

    + Handling sequences of unknown length.
    
###### **21.4**

* The idea of passing a function to another function is extremely powerful idea, and it’s one of the behaviours that makes R a functional programming language

###### **21.5**

* Mapping functions:

    + map() makes a list.
    + map_lgl() makes a logical vector.
    + map_int() makes an integer vector.
    + map_dbl() makes a double vector.
    + map_chr() makes a character vector.
  
###### **21.6**
    
* result is the original result. If there was an error, this will be NULL.

* error is an error object. If the operation was successful, this will be NULL.
